---
title: "Bass Model"
author: "Anahit Hakobyan"
date: "2/27/2023"
output:
  pdf_document: default
  html_document: default
---

```{r}
library(ggplot2)
library(ggpubr)
library(knitr)
library(diffusion)
library(readxl)
```

```{r setup, include=FALSE}
data <- read_excel("statistic_id1334833_sales-volume-of-baby-carriages-and-car-seats-for-children-in-germany-2014-2022.xlsx", sheet = 2)

head(data)
```

### Data Manipulations

Manipulating the data to keep only useful information.
```{r}
df<- data[3:11, ]
colnames(df) <- c("Year", "Car Seats", "Carriages")
df$Year[9] <- "2022"
df$Year <- as.integer(df$Year)
df$Carriages <- as.integer(df$Carriages)
df
```

### Visualizing the sales of baby carriages from 2014 to 2022

```{r}
ggplot(data = df, aes(x = Year, y = Carriages)) + geom_bar(stat = 'identity')+
  labs(title = 'Baby Carriage sales in Germany, in 1.000 units', x= ' ', y = 'sales')+
  scale_x_continuous(breaks = 2014:2022, labels = 2014:2022)+
  theme(plot.title = element_text(hjust = 0.5))
```

### Bass model parameters for the traditional baby carriage

#### Defining f(t) and F(t) functions.

bass.f - the fraction of the total market that adopts at time t; 

bass.F - the fraction of the total market that has adopted up to and including time t;

p - innovation rate;

q - imitation rate

```{r}
bass.f <- function(t,p,q){((p+q)^2/p)*exp(-(p+q)*t)/(1+(q/p)*exp(-(p+q)*t))^2}

bass.F <- function(t,p,q){
  (1-exp(-(p+q)*t))/
    (1+(q/p)*exp(-(p+q)*t))
}
```

### Model Summary and Parameter Estimation

```{r}
sales = df$Carriages
t = 1:length(sales)
bass_m = nls(sales ~ m*(((p+q)^2/p)*exp(-(p+q)*t))/
               (1+(q/p)*exp(-(p+q)*t))^2,
              start=c(list(m=sum(sales),p=0.02,q=0.4)))

summary(bass_m)
```
From the summary, we can see that the values for innovation rate, imitation rate and market potential are 0.05106, 0.09259 and 14450 respectively.
We take these values and plot the f(t) on the left side of the plot, and on the right side you can see the histogram of baby carriage sales in Germany, in 1.000 units.

```{r}
time_ad <- ggplot(data.frame(t = c(1:9)), aes(t)) +
  stat_function(fun = bass.f, args = c(p=0.05106, q=0.09259)) +
  labs(title = 'f(t)')

carriage_sales <- ggplot(data = df, aes(x = Year, y = Carriages)) +
  geom_bar(stat = 'identity') + labs(x = " ", y = "sales")

ggarrange(time_ad, carriage_sales)
```

### Estimated number of adopters by time

We take the estimated f(t) with the estimated rate of innovation and imitation and multiply it with the estimated market potential. These are plotted for different t-s on the plot as red dots.

```{r}
df$pred_sales = bass.f(1:9, p = 0.05106, q = 0.09259)*14450
ggplot(data = df, aes(x = Year, y = Carriages)) +
  geom_bar(stat = 'identity') +
  geom_point(mapping = aes(x=Year, y=pred_sales), color = 'red')+
  labs( x= ' ', y = 'sales')+scale_x_continuous(breaks = 2014:2022, labels = 2014:2022)
  
```




